\input{/Users/joshyv/Research/projects/meta/latex_paper.tex} 

\title{voltage vs. movement, take 1}

\author{us}

\begin{document}

\maketitle
% \tableofcontents
% \begin{abstract}
% 
% \end{abstract}

$T=$ number of time steps, $x$ is channels, $y$ is movement parameters. $l$ is the number of lags. lag should be between 60 and 150 msec, or so.  $l$ can be about 10, so we add 9 different lags, ranging from 60 to 150 msec.

$x \in \mc{X} =\Real_+^{96l \times T}$
$y \in \mc{Y} \subseteq \Real^{k \times T}$, $k$ can include measured stuff, plus their derivatives

things to do:

up/down-sample both $x$ and $y$ at 10kHz.

\begin{enumerate}
	\item unsupervised dimensionality reduction followed by regression: Reduce dimensionality of $x$ using sparse PCA, sparse-smooth PCA, sparse non-negative PCA.  regress on $y_t$ on $x_{t-s}$, where $s$ is about 100 msec, linear, svr, MARS, GAM (generalized additive model). loss function is mse.  concatenate trials by time. leave-some-out trials to estimate decoding accuracy.  we can further classify into 8 choices after that if we want. can repeat with 1 to $95l$ dimensions
	\item sparse CCA, free parameters: $\lambda_x$ (and perhaps $\lambda_y$), and $d$ (number of dimensions to keep).  in theory, also include $L_2$ or structured penalty if code works (laplace penalty).
	\item kalman filter: observed variable is $x$ concatenated with $y$.  hidden state is $z$:
	\begin{align}
		\dot{z} &= A z \\
		w &= C z
	\end{align}
sparse penalty on $C$, connectivity matrix, which is $96l+k \times 96l+k$.  
	\item mixed effects assuming we have 8-alternative forced choice
\end{enumerate}


% \input{body}

% \paragraph{Acknowledgments}
% \appendix
% \input{appendix}
% \clearpage

\bibliography{/Users/joshyv/Research/misc/biblist}
\addcontentsline{toc}{section}{References}
%\bibliographystyle{apalike}
\bibliographystyle{ieeetr}
%\bibliographystyle{nature}


\end{document}